### 2024-05-14 equations/equations.tex
Updated equations.tex to new reduced architecture

\subsection{Encoder}

@@

The hidden state evolves according to the following iteration formula for LSTM networks
%
\begin{align}
I^t_h[x,y,\tau] & = \sigma (i^t_h[x,y,\tau]) \\
F^t_h[x,y,\tau] & = \sigma (f^t_h[x,y,\tau]) \\
O^t_h[x,y,\tau] & = \sigma (o^t_h[x,y,\tau]) \\
C^t_h[x,y,\tau] & = F^t_h[x,y,\tau] \, C^t_h[x,y,\tau-1] + I^t_h[x,y,\tau] \, \tanh (c^t_h[x,y,\tau]) \\
H^t_h[x,y,\tau] & = O^t_h[x,y,\tau]\, \tanh(C^t_h[x,y,\tau])
\end{align}
%
going over $\tau \in [1,N_\tau]$ with initial conditions $H_h[x,y,0,t]=0$ and $C_h[x,y,0,t]=0$.
%
The stated LSTM connections of the gates can be abbreviated by a functions $L$ that returns the hidden network state for the next iteration step
%
\begin{align}
\left(\vec{H}^t[\tau], \vec{C}^t[\tau] \right) = L \left( \left\{ \vec{g}^t[\tau] \right\}, \vec{C}^t[\tau-1] \right) 
\end{align}

\subsection{Decoder}

Take last hidden state of encoder $H^t_h[x,y,N_\tau]$ and use it as input for the decoder.
%
Perform a single step (no iteration anymore!) with initial conditions $H^t_h[x,y,N_\tau]$ and $C^t_h[x,y,N_\tau]$, thus
%
\begin{align}
\tilde{g}^t_h[x,y] & =  \tilde{\mathcal{M}}^{g}_{hh'} [\xi,\eta]\, H^t_{h'}[x-\xi, y-\eta,N_\tau] \\
& +  \tilde{\mathcal{N}}^{g}_{hh'}[\xi,\eta] \, H^t_{h'}[x-\xi, y-\eta, N_\tau] + \tilde{\mathcal{B}}^g_{h}[x,y] \\
& = \tilde{\mathcal{Q}}^{g}_{hh'} [\xi,\eta]\, H^t_{h'}[x-\xi, y-\eta,N_\tau] + \tilde{\mathcal{B}}^g_{h}[x,y]
\end{align}
%
\begin{align}
\tilde{I}^t_h[x,y] & = \sigma (\tilde{i}^t_h[x,y]) \\
\tilde{F}^t_h[x,y] & = \sigma (\tilde{f}^t_h[x,y]) \\
\tilde{O}^t_h[x,y] & = \sigma (\tilde{o}^t_h[x,y]) \\
\tilde{C}^t_h[x,y] & = \tilde{F}^t_h[x,y,\tau] \, C^t_h[x,y,N_\tau] + \tilde{I}^t_h[x,y] \, \tanh (\tilde{c}^t_h[x,y]) \\
\tilde{H}^t_h[x,y] & = \tilde{O}^t_h[x,y]\, \tanh(\tilde{C}^t_h[x,y])
\end{align}
%
The action of the decoder can be compactly written as
\begin{align}
\left(\tilde{\vec{H}}^t, \tilde{\vec{C}}^t \right) = L \left( \left\{ \tilde{\vec{g}}^t \right\}, \vec{C}^t[N_\tau] \right) 
\end{align}

@@

Choose $a \in [1, 512]$, $b \in [1, 256]$ then
%
\begin{align}
R_r[t] = \mathcal{W}^{3}_{rb}\mathrm{ReLU}\left(\mathcal{W}^{2}_{ba}\mathrm{ReLU}\left(\mathcal{W}^{1}_{ah} [x,y] \tilde{H}^t_h[x,y]\right)\right)
\end{align}
%
with $r \in [1, 97]$.

@@

We can write our final result $R_r[t]$ for the $r$-th river as a function $M_r$ (for model) which itself is a nested function call of the $r$-th component of the fully connected layer $F$, the decoder $D$ and the encoder $E$ on a given input time sequence  $\{X^t_k[x,y,\tau]\}$, i.e.
\begin{tcolorbox}[ams align]
R_r[t] = M_r(\{X^t_k[x,y,\tau]\}) = F_r(D(E(\{X^t_k[x,y,\tau]\})))
\end{tcolorbox}
%
The idea is to approximate each $R_r[t]$ like
%
\begin{tcolorbox}[ams align]
R_r[t] \approx A_r[t] = a_r + \omega_{rk}[x,y,\tau] X^t_k[x,y,\tau]
\end{tcolorbox}
%
or expressed in continuous variables
\begin{align}
A_r(t) = a_r + \intop_{0}^{\tau_{\text{max}}} \text{d}\tau \intop_{\mathbb{R}^2} \text{d}x \text{d}y \, \omega_{rk}(x,y,\tau) X^t_k(x,y,\tau)
\end{align}
%
which means that the runoff is approximately determined by the spatially dependent memory kernel that weights the influence of each time instance of each channel back to the time $t-\tau_{\text{max}}$.

@@

In order to keep the overview it is beneficial to write the output of each function in the nest as individual variables, i.e.
\begin{tcolorbox}[ams align]
\{\epsilon_{sh}[x,y]\} = E(\{X_k[x,y,\tau]\}) \\
\{\tilde{H}_h[x,y]\} = D(\{\epsilon^s_h[x,y]\}) \\
\phi_r = F_r(\{\tilde{H}_h[x,y]\})
\end{tcolorbox}
where the additional index $s$ in $\epsilon_{sh}[x,y]$ goes over the internal states of the encoder's output, i.e. 
\begin{tcolorbox}[ams align]
\epsilon_{1h}[x,y] = C_h[x,y,N_\tau], \quad \epsilon_{2h}[x,y] = H_h[x,y,N_\tau].
\end{tcolorbox}
%
Note that the superscript $t$ is now omitted in the internal states since we calculate these quantities with respect to the reference sequence $\{X_k[x,y,\tau]\}$ that should not be connected to any specific time.
%
Note further that the decoder's output state $\tilde{H}_h[x,y]$ has already been defined above.

As a first step we can now further evaluate the derivative via the chain rule
\begin{align}
\omega_{rk}[x,y,\tau] = \del{ M_r(\{X_k[x,y,\tau]\})}{X_k[x,y,\tau]} = \del{\phi_r}{\tilde{H}_{h''}[x'',y'']} \del{\tilde{H}_{h''}[x'',y'']}{\epsilon_{s'h'}[x',y']} \del{\epsilon_{s'h'}[x',y']}{X_k[x,y,\tau]}
\end{align}
%
The next task is to unfold the dependence of $\epsilon_{sh}[x,y]$ on $\{X_k[x,y,\tau]\}$.
%
For that purpose we define the action of one ConvLSTM cell as function $K$. 
Then $\epsilon_{sh}[x,y]$ is the $N_\tau$-fold nested function
\begin{align}
\epsilon_{sh}[x,y] = E(\{X_k[x,y,\tau]\}) = K(\{X_k[x,y,N_\tau]\},K(\{X_k[x,y,N_\tau-1]\},\ldots, \{X_k[x,y,2]\}, K(\{X_k[x,y,1]\},0)\ldots ))
\end{align}
%
We can now define the output of the $K$-calls recursively for a fixed $\tau$ as 
%
\begin{align}
\{\kappa_{sh}[x,y,\tau]\} = K\left(\{X_k[x,y,\tau]\}, \{\kappa_{sh}[x,y,\tau-1]\} \right)
\end{align}
with $\kappa_{sh}[x,y,0]=0$ and $\kappa_{sh}[x,y,N_\tau]=\epsilon_{sh}[x,y]$.
%
Now we can use the chain rule to calculate the derivative of $\epsilon_{s'h'}[x',y']$ with respect to $X_k[x,y,\tau]$ for a specific $\tau$
%
\begin{align}
 \del{\epsilon_{s'h'}[x',y']}{X_k[x,y,\tau]} = \left( \prod_{j=\tau}^{N_\tau-1} \del{\kappa_{s_{j+1}h_{j+1}}[x_{j+1},y_{j+1},j+1]}{\kappa_{s_{j}h_{j}}[x_{j},y_{j},j]} \right) \del{\kappa_{s_{\tau}h_{\tau}}[x_{\tau},y_{\tau},\tau]}{X_k[x,y,\tau]}
\end{align}
with the boundary conditions for the auxiliary indices $x_{N_\tau}\equiv x', y_{N_\tau} \equiv y', h_{N_\tau} \equiv h', s_{N_\tau} \equiv s'$.
%
This can be inserted into the formula for $\omega_{rk}[x,y,\tau]$ yielding
\begin{tcolorbox}[ams align]
\omega_{rk}[x,y,\tau] = \del{\phi_r}{\tilde{H}_{h''}[x'',y'']} \del{\tilde{H}_{h''}[x'',y'']}{\epsilon_{s_{N_\tau} h_{N_\tau}}[x_{N_\tau},y_{N_\tau}]} \left( \prod_{j=\tau}^{N_\tau-1} \del{\kappa_{s_{j+1}h_{j+1}}[x_{j+1},y_{j+1},j+1]}{\kappa_{s_{j}h_{j}}[x_{j},y_{j},j]} \right) \del{\kappa_{s_{\tau}h_{\tau}}[x_{\tau},y_{\tau},\tau]}{X_k[x,y,\tau]}
\end{tcolorbox}

@@

Now that we have expressions for the derivatives we can give them names
\begin{tcolorbox}[ams align]
\Lambda_{s's,h'h}[x', x, y', y, j] = \del{\kappa_{s'h'}[x',y',j]}{\kappa_{sh}[x,y,j-1]}  \\
\lambda_{s'h',k}[x', x, y', y, \tau] = \del{\kappa_{s'h'}[x',y',\tau]}{X_k[x,y,\tau]} 
\end{tcolorbox}
and insert it into the full expression
\begin{align}
\omega_{rk}[x,y,\tau] = \del{\phi_r}{\tilde{H}_{h''}[x'',y'']} \del{\tilde{H}_{h''}[x'',y'']}{\epsilon_{s_{N_\tau} h_{N_\tau}}[x_{N_\tau},y_{N_\tau}]} \left( \prod_{j=\tau}^{N_\tau-1} \Lambda_{s_{j+1}s_j,h_{j+1}h_j}[x_{j+1}, x_j, y_{j+1}, y_j, j+1] \right)
\lambda_{s_\tau h_\tau,k}[x_\tau, x, y_\tau, y, \tau]
\end{align}
%
To further shorten the expression we can formally carry out the product as 
\begin{align}
\chi_{s_{n} h_{n},k}[x_{n}, x, y_{n}, y, n, \tau] = \left( \prod_{j=\tau}^{n-1} \Lambda_{s_{j+1}s_j,h_{j+1}h_j}[x_{j+1}, x_j, y_{j+1}, y_j, j+1] \right)
\lambda_{s_\tau h_\tau,k}[x_\tau, x, y_\tau, y, \tau]
\end{align}
with $\tau \leq n \leq N_\tau$ then
%
\begin{tcolorbox}[ams align]
\chi_{s_{n+1} h_{n+1},k}[x_{n+1}, x, y_{n+1}, y, n+1, \tau] =  \Lambda_{s_{n+1}s_n,h_{n+1}h_n}[x_{n+1}, x_n, y_{n+1}, y_n, n+1] 
\chi_{s_{n} h_{n},k}[x_{n}, x, y_{n}, y, n, \tau]
\end{tcolorbox}
%
for $n=\tau,\ldots N_\tau-1$ and $\chi_{s_{\tau} h_{\tau},k}[x_{\tau}, x, y_{\tau}, y, \tau, \tau] = \lambda_{s_\tau h_\tau,k}[x_\tau, x, y_\tau, y, \tau]$.

The next task is to evaluate the derivative of the decoder with respect to the encoders output.
%
Since the decoder is itself a ConvLSTM cell with input from encoders last hidden state we can write
\begin{align}
\{\tilde{H}_{h}[x,y]\} = \tilde{K}_2 \left( \{ \epsilon_{2 h}[x,y]\}, \{ \epsilon_{s h}[x,y]\} \right)
\end{align}
%
Following the same line of reasoning as above we obtain for the derivatives
%
\begin{tcolorbox}[ams align]
\del{\tilde{H}_{h'}[x',y']}{\epsilon_{1h}[x,y]} = \del{\tilde{H}_{h'}[x',y']}{C_h[x,y,N_\tau]}  & = \frac{\tilde{O}_{h'}[x',y'] \tilde{F}_{h'}[x',y']}{\cosh^2(\tilde{C}_{h'}[x',y'])}  \delta_{hh'}\delta_{xx'}\delta_{yy'} \\
\del{\tilde{H}_{h'}[x',y']}{\epsilon_{2h}[x,y]} = \del{\tilde{H}_{h'}[x',y']}{H_h[x,y,N_\tau]}     & = \dot{\sigma}(\tilde{o}_{h'}[x',y'])\tanh(\tilde{C}_{h'}[x',y']) \tilde{\mathcal{Q}}^{o}_{h'h}[x'-x,y'-y] \\
& + \frac{\sigma(\tilde{o}_{h'}[x',y'])}{\cosh^2(\tilde{C}_{h'}[x',y'])} \tilde{\Lambda}_{1,2,h'h}[x', x, y', y]
\end{tcolorbox}
%
with
\begin{align}
\tilde{\Lambda}_{1,2,h'h}[x', x, y', y] & = \dot{\sigma}(\tilde{f}_{h'}[x',y']) C_{h'}[x',y',N_\tau] \tilde{\mathcal{Q}}^{f}_{h'h}[x'-x,y'-y]\\
& + \dot{\sigma}(\tilde{i}_{h'}[x',y']) \tanh(\tilde{c}_{h'}[x',y'])\tilde{\mathcal{Q}}^{i}_{h'h}[x'-x,y'-y]\\
& +  \frac{\sigma(\tilde{i}_{h'}[x',y'])}{\cosh^2(\tilde{c}_{h'}[x',y'])} \tilde{\mathcal{Q}}^{c}_{h'h}[x'-x,y'-y]
\end{align}
%
Now we can also rename these derivatives as
\begin{tcolorbox}[ams align]
\tilde{\chi}_{s_{N_\tau}h_{N_\tau}, h''}[x'', x_{N_\tau}, y'', y_{N_\tau}] = \del{\tilde{H}_{h''}[x'',y'']}{\epsilon_{s_{N_\tau} h_{N_\tau}}[x_{N_\tau},y_{N_\tau}]}
\end{tcolorbox}
%
and insert into the full expression
%
\begin{align}
\omega_{rk}[x,y,\tau] = \del{\phi_r}{\tilde{H}_{h''}[x'',y'']} \tilde{\chi}_{s_{N_\tau}h_{N_\tau}, h''}[x'', x_{N_\tau}, y'', y_{N_\tau}] \chi_{s_{N_\tau} h_{N_\tau},k}[x_{N_\tau}, x, y_{N_\tau}, y, N_\tau, \tau]
\end{align}
%
If we define the product 
%
\begin{tcolorbox}[ams align]
\Xi_{h''k}[x'', x, y'', y, \tau] = \tilde{\chi}_{s_{N_\tau}h_{N_\tau}, h''}[x'', x_{N_\tau}, y'', y_{N_\tau}] \chi_{s_{N_\tau} h_{N_\tau},k}[x_{N_\tau}, x, y_{N_\tau}, y, N_\tau, \tau]
\end{tcolorbox}
%
we can write
\begin{tcolorbox}[ams align]
\omega_{rk}[x,y,\tau] = \del{\phi_r}{\tilde{H}_{h''}[x'',y'']} \Xi_{h''k}[x'', x, y'', y, \tau]
\end{tcolorbox}

The remaining task is to find the derivative of the fully connected layser with respect to the decoder's output.
%
For this purpose we define gain the output variables of the nested ReLU functions as individual variables, i.e.
\begin{tcolorbox}[ams align]
\rho^1_a & = \mathcal{W}^{1}_{ah} [x,y] \tilde{H}_h[x,y] \\
\rho^2_b & = \mathcal{W}^{2}_{ba} \mathrm{ReLU}\left(\rho^1_a\right) \\
\phi_r & = \mathcal{W}^{3}_{rb} \mathrm{ReLU}\left(\rho^2_b \right)
\end{tcolorbox}
%
With these definitions we can write after using the chain rule
\begin{align}
\del{\phi_r}{\tilde{H}_{h''}[x'',y'']} = \del{\phi_r}{\rho^2_{b'}} \del{\rho^2_{b'}}{\rho^1_{a'}} \del{\rho^1_{a'}}{\tilde{H}_{h''}[x'',y'']}
\end{align}
The individual derivatives can be easily carried out by noting $\partial \mathrm{ReLU}(x) / \partial x = \theta(x)$ which is the Heaviside step function
\begin{align}
\del{\phi_r}{\rho^2_{b'}} & = \mathcal{W}^{3}_{rb'} \theta \left( \rho^2_{b'} \right)  \\
 \del{\rho^2_{b'}}{\rho^1_{a'}} & =  \mathcal{W}^{2}_{b'a'} \theta \left( \rho^1_{a'} \right) \\
 \del{\rho^1_{a'}}{\tilde{H}_{h''}[x'',y'']} & = \mathcal{W}^{1}_{a'h''} [x'',y'']
\end{align}
%
\begin{tcolorbox}[ams align]
\del{\phi_r}{\tilde{H}_{h''}[x'',y'']} = \mathcal{W}^{3}_{rb'} \theta \left( \rho^2_{b'} \right) \cdot  \mathcal{W}^{2}_{b'a'} \theta \left( \rho^1_{a'} \right) \cdot \mathcal{W}^{1}_{a'h''} [x'',y''] = \Omega_{r h''}[x'',y'']
\end{tcolorbox}

As the final result we can then write 
%
\begin{tcolorbox}[ams align]
\omega_{rk}[x,y,\tau] = \Omega_{r h''}[x'',y''] \cdot \Xi_{h''k}[x'', x, y'', y, \tau]
\end{tcolorbox}

>>>>

\subsection{ConvLSTM}

@@

The hidden state evolves according to the following iteration formula for LSTM networks
%
\begin{align}
I^t_h[x,y,\tau] & = \sigma (i^t_h[x,y,\tau]) \\
F^t_h[x,y,\tau] & = \sigma (f^t_h[x,y,\tau]) \\
O^t_h[x,y,\tau] & = \sigma (o^t_h[x,y,\tau]) \\
C^t_h[x,y,\tau] & = F^t_h[x,y,\tau] \, C^t_h[x,y,\tau-1] + I^t_h[x,y,\tau] \, \tanh (c^t_h[x,y,\tau]) \\
H^t_h[x,y,\tau] & = O^t_h[x,y,\tau]\, \tanh(C^t_h[x,y,\tau])
\end{align}
%
going over $\tau \in [1,N_\tau]$ with initial conditions $H_h[x,y,0,t]=0$ and $C_h[x,y,0,t]=0$.
%
The stated LSTM connections of the gates can be abbreviated by a functions $L$ that returns the hidden network state for the next iteration step
%
\begin{align}
\left(\vec{H}^t, \vec{C}^t \right) = L \left( \vec{X}^t[N_\tau], L \left( \vec{X}^t[N_\tau-1], \ldots L \left( \vec{X}^t[1], (\vec{H}^t[0], \vec{C}^t[0] \right) \ldots \right) \right) \ ,
\end{align}
where $L\left(\vec{X}^t[\tau], \left(\vec{H}^t[\tau-1], \vec{C}^t[\tau-1] \right) \right)$ represents LSTM network equations and the initial conditions are chosen as $\vec{H}^t[0]=\vec{C}^t[0]=0$ and with the abbreviation for final output $\vec{H}^t[N_\tau] \equiv \vec{H}^t$ and $\vec{C}^t[N_\tau] \equiv \vec{C}^t$

@@

Choose $a \in [1, 512]$, $b \in [1, 256]$ then
%
\begin{align}
R_r[t] = \mathcal{W}^{3}_{rb}\mathrm{ReLU}\left(\mathcal{W}^{2}_{ba}\mathrm{ReLU}\left(\mathcal{W}^{1}_{ah} [x,y] H^t_h[x,y] + \mathcal{B}^1_a\right) + \mathcal{B}^2_b \right) + \mathcal{B}^3_r
\end{align}
%
with $r \in [1, 97]$.

@@

We can write our final result $R_r[t]$ for the $r$-th river as a function $M_r$ (for model) which itself is a nested function call of the $r$-th component of the fully connected layer $F_r$ and the ConvLSTM $K$ on a given input time sequence  $\{X^t_k[x,y,\tau]\}$, i.e.
\begin{tcolorbox}[ams align]
R_r[t] = M_r(\{X^t_k[x,y,\tau]\}) = F_r(K(\{X^t_k[x,y,\tau]\}))
\end{tcolorbox}
%
The idea is to approximate each $R_r[t]$ like
%
\begin{tcolorbox}[ams align]
R_r[t] \approx A_r[t] = a_r + \omega_{rk}[x,y,\tau] X^t_k[x,y,\tau]
\end{tcolorbox}
%
or expressed in continuous variables
\begin{align}
A_r(t) = a_r + \intop_{0}^{\tau_{\text{max}}} \text{d}\tau \intop_{\mathbb{R}^2} \text{d}x \text{d}y \, \omega_{rk}(x,y,\tau) X^t_k(x,y,\tau)
\end{align}
%
which means that the runoff is approximately determined by the spatially dependent memory kernel that weights the influence of each time instance of each channel back to the time $t-\tau_{\text{max}}$.

@@

In order to keep the overview it is beneficial to write the output of each function in the nest as individual variables, i.e.
\begin{tcolorbox}[ams align]
\{H_h[x,y]\} = K(\{X_k[x,y,\tau]\}) \\
\phi_r = F_r(\{H_h[x,y]\})
\end{tcolorbox}

%
Note that the superscript $t$ is now omitted in the internal states since we calculate these quantities with respect to the reference sequence $\{X_k[x,y,\tau]\}$ that should not be connected to any specific time.

As a first step we can now further evaluate the derivative via the chain rule
\begin{align}
\omega_{rk}[x,y,\tau] = \del{ M_r(\{X_k[x,y,\tau]\})}{X_k[x,y,\tau]} = \del{\phi_r}{H_{h'}[x',y']} \del{H_{h'}[x',y']}{X_k[x,y,\tau]}
\end{align}
%
The next task is to unfold the dependence of $H_{h}[x,y]$ on $\{X_k[x,y,\tau]\}$.
%
For that purpose we define the action of one ConvLSTM cell as function $L$. 
Then $\epsilon_{sh}[x,y]$ is the $N_\tau$-fold nested function
\begin{align}
H_{h}[x,y] = K(\{X_k[x,y,\tau]\}) = L(\{X_k[x,y,N_\tau]\},L(\{X_k[x,y,N_\tau-1]\},\ldots, \{X_k[x,y,2]\}, L(\{X_k[x,y,1]\},0)\ldots ))
\end{align}
%
We can now define the output of the $L$-calls recursively for a fixed $\tau$ as 
%
\begin{align}
\{\kappa_{sh}[x,y,\tau]\} = L\left(\{X_k[x,y,\tau]\}, \{\kappa_{sh}[x,y,\tau-1]\} \right)
\end{align}
where the additional index $s$ labels the two outputs of the $L$-function, i.e. $C_{h}[x,y,\tau]=\kappa_{1h}[x,y,\tau]$ and $H_{h}[x,y,\tau]=\kappa_{2h}[x,y,\tau]$.
The initial condition is $\kappa_{sh}[x,y,0]=0$ and the endpoint is by construction $\kappa_{2h}[x,y,N_\tau]=H_{h}[x,y]$.
%
Now we can use the chain rule to calculate for a specific $\tau$
%
\begin{align}
 \del{H_{h'}[x',y']}{X_k[x,y,\tau]} = \left. \del{\kappa_{s' h'}[x',y',N_\tau]}{X_k[x,y,\tau]} \right |_{s'=2} = \left. \left( \prod_{j=\tau}^{N_\tau-1} \del{\kappa_{s_{j+1}h_{j+1}}[x_{j+1},y_{j+1},j+1]}{\kappa_{s_{j}h_{j}}[x_{j},y_{j},j]} \right) \right |_{s_{N_\tau} = s' = 2} \del{\kappa_{s_{\tau}h_{\tau}}[x_{\tau},y_{\tau},\tau]}{X_k[x,y,\tau]}
\end{align}
with the boundary conditions for the auxiliary indices $x_{N_\tau}\equiv x', y_{N_\tau} \equiv y', h_{N_\tau} \equiv h', s_{N_\tau} \equiv s'$.
%
This can be inserted into the formula for $\omega_{rk}[x,y,\tau]$ yielding
\begin{tcolorbox}[ams align]
\omega_{rk}[x,y,\tau] = \del{\phi_r}{H_{h'}[x',y']} \left.\left( \prod_{j=\tau}^{N_\tau-1} \del{\kappa_{s_{j+1}h_{j+1}}[x_{j+1},y_{j+1},j+1]}{\kappa_{s_{j}h_{j}}[x_{j},y_{j},j]} \right) \right |_{s_{N_\tau} = s' = 2} \del{\kappa_{s_{\tau}h_{\tau}}[x_{\tau},y_{\tau},\tau]}{X_k[x,y,\tau]}
\end{tcolorbox}

@@

Now that we have expressions for the derivatives we can give them names
\begin{tcolorbox}[ams align]
\Lambda_{s's,h'h}[x', x, y', y, j] = \del{\kappa_{s'h'}[x',y',j]}{\kappa_{sh}[x,y,j-1]}  \\
\lambda_{s'h',k}[x', x, y', y, \tau] = \del{\kappa_{s'h'}[x',y',\tau]}{X_k[x,y,\tau]} 
\end{tcolorbox}
and insert it into the full expression
\begin{align}
\omega_{rk}[x,y,\tau] = \del{\phi_r}{\tilde{H}_{h'}[x',y']} \left. \left( \prod_{j=\tau}^{N_\tau-1} \Lambda_{s_{j+1}s_j,h_{j+1}h_j}[x_{j+1}, x_j, y_{j+1}, y_j, j+1] \right) \right |_{s_{N_\tau} = s' = 2} 
\lambda_{s_\tau h_\tau,k}[x_\tau, x, y_\tau, y, \tau]
\end{align}
%
To further shorten the expression we can formally carry out the product as 
\begin{align}
\chi_{s_{n} h_{n},k}[x_{n}, x, y_{n}, y, n, \tau] = \left( \prod_{j=\tau}^{n-1} \Lambda_{s_{j+1}s_j,h_{j+1}h_j}[x_{j+1}, x_j, y_{j+1}, y_j, j+1] \right)
\lambda_{s_\tau h_\tau,k}[x_\tau, x, y_\tau, y, \tau]
\end{align}
with $\tau \leq n \leq N_\tau$ then
%
\begin{tcolorbox}[ams align]
\chi_{s_{n+1} h_{n+1},k}[x_{n+1}, x, y_{n+1}, y, n+1, \tau] =  \Lambda_{s_{n+1}s_n,h_{n+1}h_n}[x_{n+1}, x_n, y_{n+1}, y_n, n+1] 
\chi_{s_{n} h_{n},k}[x_{n}, x, y_{n}, y, n, \tau]
\end{tcolorbox}
%
for $n=\tau,\ldots N_\tau-1$ and $\chi_{s_{\tau} h_{\tau},k}[x_{\tau}, x, y_{\tau}, y, \tau, \tau] = \lambda_{s_\tau h_\tau,k}[x_\tau, x, y_\tau, y, \tau]$.

%
and insert into the full expression
%
\begin{align}
\omega_{rk}[x,y,\tau] = \del{\phi_r}{H_{h'}[x',y']} \chi_{2,h',k}[x', x, y', y, N_\tau, \tau]
\end{align}
%
If we define the symbol 
%
\begin{tcolorbox}[ams align]
\Xi_{h'k}[x', x, y', y, \tau] =  \chi_{2,h',k}[x', x, y', y, N_\tau, \tau]
\end{tcolorbox}
%
we can write
\begin{tcolorbox}[ams align]
\omega_{rk}[x,y,\tau] = \del{\phi_r}{H_{h'}[x',y']} \Xi_{h'k}[x', x, y', y, \tau]
\end{tcolorbox}

The remaining task is to find the derivative of the fully connected layser with respect to the decoder's output.
%
For this purpose we define gain the output variables of the nested ReLU functions as individual variables, i.e.
\begin{tcolorbox}[ams align]
\rho^1_a & = \mathcal{W}^{1}_{ah} [x,y] H_h[x,y] + \mathcal{B}^1_a \\
\rho^2_b & = \mathcal{W}^{2}_{ba} \mathrm{ReLU}\left(\rho^1_a\right) + \mathcal{B}^2_b \\
\phi_r & = \mathcal{W}^{3}_{rb} \mathrm{ReLU}\left(\rho^2_b \right) + \mathcal{B}^3_r
\end{tcolorbox}
%
With these definitions we can write after using the chain rule
\begin{align}
\del{\phi_r}{H_{h'}[x',y']} = \del{\phi_r}{\rho^2_{b'}} \del{\rho^2_{b'}}{\rho^1_{a'}} \del{\rho^1_{a'}}{\tilde{H}_{h''}[x'',y'']}
\end{align}
The individual derivatives can be easily carried out by noting $\partial \mathrm{ReLU}(x) / \partial x = \theta(x)$ which is the Heaviside step function
\begin{align}
\del{\phi_r}{\rho^2_{b'}} & = \mathcal{W}^{3}_{rb'} \theta \left( \rho^2_{b'} \right)  \\
 \del{\rho^2_{b'}}{\rho^1_{a'}} & =  \mathcal{W}^{2}_{b'a'} \theta \left( \rho^1_{a'} \right) \\
 \del{\rho^1_{a'}}{H_{h'}[x',y']} & = \mathcal{W}^{1}_{a'h'} [x',y']
\end{align}
%
\begin{tcolorbox}[ams align]
\del{\phi_r}{H_{h'}[x',y']} = \mathcal{W}^{3}_{rb'} \theta \left( \rho^2_{b'} \right) \cdot  \mathcal{W}^{2}_{b'a'} \theta \left( \rho^1_{a'} \right) \cdot \mathcal{W}^{1}_{a'h'} [x',y'] = \Omega_{r h'}[x',y']
\end{tcolorbox}

As the final result we can then write 
%
\begin{tcolorbox}[ams align]
\omega_{rk}[x,y,\tau] = \Omega_{r h'}[x',y'] \cdot \Xi_{h'k}[x', x, y', y, \tau]
\end{tcolorbox}
